\clearpage
\section*{Authors}
{\normalsize 

\textbf{Sherman Robinson} (\href{mailto:s.robinson@cgiar.org}{s.robinson@cgiar.org}) is a Research Fellow Emeritus at the Director General's Office of the International Food Policy Research Institute, Washington, D.C., USA. 

\vspace{0.07cm}

\textbf{Shahnila Dunston} was formerly a Senior Research Analyst at the Foresight and Policy Modeling unit of the International Food Policy Research Institute, Washington, D.C., USA. Shahnila is an Applied Economist - Climate Fellow at the Economic Research Service of the United States Department of Agriculture.

\vspace{0.07cm}


\textbf{Abhijeet Mishra} (\href{mailto:a.mishra@cgiar.org}{a.mishra@cgiar.org}) is an Associate Research Fellow at the Foresight and Policy Modeling unit of the International Food Policy Research Institute, Washington, D.C., USA.

\vspace{0.07cm}


\textbf{Timothy B. Sulser} (\href{mailto:t.sulser@cgiar.org}{t.sulser@cgiar.org}) is a Senior Scientist at the Foresight and Policy Modeling unit of the International Food Policy Research Institute, Washington, D.C., USA.

\vspace{0.07cm}


\textbf{Daniel Mason-D’Croz} was formerly a Senior Research Analyst at the Environment and Production Technology Division the International Food Policy Research Institute, Washington, D.C., USA. Daniel is a Senior Research Associate at the Department of Global Development of the College of Agriculture and Life Sciences at Cornell University, Ithaca, New York, USA.

\vspace{0.07cm}


\textbf{Richard Robertson} (\href{mailto:r.robertson@cgiar.org}{r.robertson@cgiar.org}) is a Research Fellow at the Foresight and Policy Modeling unit of the International Food Policy Research Institute, Washington, D.C., USA.

\vspace{0.07cm}


\textbf{Nicola Cenacchi} (\href{mailto:n.cenacchi@cgiar.org}{n.cenacchi@cgiar.org}) is a Senior Research Analyst at the Foresight and Policy Modeling unit of the International Food Policy Research Institute, Washington, D.C., USA.

\vspace{0.07cm}


\textbf{Tim Thomas} (\href{mailto:tim.thomas@cgiar.org}{tim.thomas@cgiar.org}) is a Senior Research Fellow at the Foresight and Policy Modeling unit of the International Food Policy Research Institute, Washington, D.C., USA.

\vspace{0.07cm}


\textbf{Tingju Zhu} was formerly a Research fellow in the Environment and Production Technology Division of the International Food Policy Research Institute, Washington, D.C., USA.

\vspace{0.07cm}


\textbf{Arthur Gueneau} was formerly a Research Analyst in the Development Strategy and Governance Division of the International Food Policy Research Institute, Washington, D.C., USA.

\vspace{0.07cm}


\textbf{Gauthier Pitois} was formerly a Research Analyst in the Development Strategy and Governance Division of the International Food Policy Research Institute, Washington, D.C., USA.

\vspace{0.07cm}


\textbf{Keith Wiebe} (\href{mailto:k.wiebe@cgiar.org}{k.wiebe@cgiar.org}) is a Senior Research Fellow at the Foresight and Policy Modeling unit of the International Food Policy Research Institute, Washington, D.C., USA and Lead of the CGIAR Research Initiative on Foresight.

\vspace{0.07cm}


\textbf{Mark Rosegrant} (\href{mailto:m.rosegrant@cgiar.org}{m.rosegrant@cgiar.org}) is an IFPRI–Emeritus Fellow at the Director General's Office of the International Food Policy Research Institute, Washington, D.C., USA.
}
\thispagestyle{empty}% Reset page style to 'empty"